{\normalsize Seminar: Formal Specification} \\[1ex] Security of Multithreaded Programs by Compilation\cite{Barthe07}

### 2012-01-14 paper/paper.tex
added paragraphs about 'always high' and 'hidden' threads

>>>>

At this point a first simplification can be made. Looking a state $s$ we can
first extract the active threads (\texttt{s.act}) by taking the domain of the first
component. According to a security environment we can classify these threads,
with respect to their current program point (\texttt{s.pc(tid)} where $tid \in Thread$),
into \textit{low} threads iff the current program point is low. In \textit{high}
threads iff the current program point is high. In \textit{always high} threads
iff the current program point is always high and in \textit{hidden} threads, iff
the current program point is high but not always high.

The latte two are the interesting ones. If a thread is \textit{always high} it
can not leaks any information into low, because it never only gets in touch
with low program points. So these threads can safely be interleaved by the
scheduler.

The \textit{hidden} threads are the ones we have to care about. These contain
obviously high information in the current program point, but have afterwards
instructions that deal with low information. Since the attacker can watch the
low part of the memory, chances are good that he can deduce high information
through changing low outputs. To prevent indirect flows that are introduced by
these hidden threads, the scheduler will be modified to treat these threads
in a special way. This will be done by 'hiding' these threads, therefore comes
the name of them.
